### 2019-02-07 tex_v2/manuscript.tex
added analysis pipeline, data, and plots

		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
		Consequently, there was a negative correlation between utlimate tensile strenth of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
		In other words, UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
		These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

>>>>

		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
		Consequently, there was a negative correlation between utlimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
		In other words, UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
		These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.
